---
title: "COVID-19"
author: "Manuel Mariscal"
date: "19/3/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This presentation is part of the Developing Data Products Coursera.org course project submission.

It is an R Presentation generated with RStudio.

The Shiny application pitched by this presentation is at https://mmriscal.shinyapps.io/COVID/

## The app

The app plots different graphics of the evolution of COVID-19 in China, Spain and Italy. The user
can select what country must be plotted and the type of graphic. 

The user can gather information about new cases, new deaths, total cases or total deaths related to 
the virus. All the information is continuosly updated online.

More information about the data can be found in: https://covid.ourworldindata.org


## Code 1

I found a lot of difficulties in downloading the dataset while the app is running in shinyapp.io. Finally,
the following code worked:

```{r eval=FALSE, echo=TRUE}
data <- read.csv("https://covid.ourworldindata.org/data/full_data.csv")
```

I also struggled with the user interface. I decided to use columns:

```{r eval=FALSE, echo=TRUE}
fluidRow
    (
        column(3, offset = 1,
               h4("Select country"),
``` 

## More information

You can e-mail me at mmriscal@gmail.com for further information. All the code can be found in 




